Team size and composition in home health care

### 2023-10-19 paper-presentation/paper-presentation.qmd
Adde slides

@@

@@

*The complexity of the number of interactions for a team of size [$M$]{style="color: red;"} is $O(M^2)$. By splitting the team into [$k$]{style="color: red;"} sub-teams, managed by one mediator, the number of interactions can be reduced by a factor [$k$]{style="color: red;"} as [$M$]{style="color: red;"} grows large.*

@@

# Discussion

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

# Conclusion

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

>>>>

![](images/database.png)

## Data understanding

| Area type | Teams | Planned care \n(hrs/wk) |    Clients | Clients/km^2^ |
|-----------|------:|------------------------:|-----------:|--------------:|
| Urban     |    26 |                238 (51) | 221 (51.4) |     71 (31.4) |
| Suburban  |    18 |                224 (54) | 238 (61.3) |      11 (5.4) |
| Rural     |    11 |                213 (46) | 176 (53.6) |       3 (1.1) |

: General information per area type for the years 2020, 2021; all numerical values (except team count) represent the mean, with standard deviation in brackets.

@@

![](images/durationperday.png)

## Data preparation

![](images/meansvar.png)

## Data preparation

![](images/los.png)

@@

*The complexity of the number of interactions for a team of size* [$M$]{style="color: red;"} is $O(M^2)$. By splitting the team into [$k$]{style="color: red;"} sub-teams, managed by one mediator, the number of interactions can be reduced by a factor [$k$]{style="color: red;"} as [$M$]{style="color: red;"} grows large.

@@

# Practice based scenarios

::: columns
::: {.column width="35%"}
![](images/map.png){width="300"}
:::

::: {.column width="65%"}
![](images/scenarios.png){width="900"}
:::
:::

# Questions
